Temporality is Important for Networks of Hospital Patient Transfers

### 2024-09-26 reports/report.qmd
report minor edits (+refs)

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf: default
---

@@

@@

@@

In the full network, we can roughly

>>>>

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf: default
bibliography: refs.bib
csl: plos.csl
---

@@

Antimicrobial resistance poses a great threat to human health and development. [@murray_global_2022]
Globally, it poses a large burden, operationally and economically, on hospital systems.

@@

<!-- I don't know why, but the first invocation of the dot engine craps out -->
```{dot}
```

@@

For a larger network, the number of possible paths causes complications for explicit computation of the effect, but we can always expect it to follow a similar principle, where splitting transfers into a direct path and a slower indirect path will add to the expected hitting time.
